**Urinary Vitamin D Binding Protein as a Potential Biomarker for Nephropathy in Patients at risk for Type 2 Diabetes**: The Prospective Metabolism and Islet Cell Evaluation (PROMISE) cohort study.

### 2017-05-23 doc/adaAbstract.Rmd
gee model for ada abstract with new covariates

```{r mason}

gee <- ds %>%
  dplyr::mutate(
  udbpBase = ifelse(fVN == "Baseline", UDBP, NA),
  ageBase = ifelse(fVN == "Baseline", Age, NA),
  fDM = relevel(as.factor(DM), "1")
  # Ethnicity = ifelse(Ethnicity == "European", Ethnicity, "Other"),
  ) %>%
  dplyr::filter(!(fVN == "Baseline" &
                    acrStatus == "Macroalbuminuria")) %>%
  dplyr::filter(!(fVN == "Baseline" & eGFRStatus == "Moderate")) %>%
  dplyr::arrange(SID, fVN) %>%
  dplyr::group_by(SID) %>%
  tidyr::fill(udbpBase, ageBase) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(UDBP = UDBP/1000) %>%
  dplyr::arrange(SID, VN) %>%
  mason_gee(
  yvars = c("ACR", "eGFR"),
  xvars = "UDBP",
  covars = c("VN", "ageBase", "fDM")
  )
```

>>>>

```{r gee}

gee <- ds %>%
  dplyr::mutate(
  udbpBase = ifelse(fVN == "Baseline", UDBP, NA),
  ageBase = ifelse(fVN == "Baseline", Age, NA),
  DM = ifelse(DM == 1, "diabetes", "non_dia"),
  fDM = relevel(as.factor(DM), "non_dia"),
  Ethnicity = ifelse(Ethnicity == "European", Ethnicity, "Other"),
  Ethnicity = relevel(as.factor(Ethnicity), "Other")
  ) %>%
  dplyr::filter(!(fVN == "Baseline" &
                    acrStatus == "Macroalbuminuria")) %>%
  dplyr::filter(!(fVN == "Baseline" & eGFRStatus == "Moderate")) %>%
  dplyr::arrange(SID, fVN) %>%
  dplyr::group_by(SID) %>%
  tidyr::fill(udbpBase, ageBase) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(UDBP = UDBP/1000) %>%
  dplyr::arrange(SID, VN) %>%
  mason::design("gee") %>% 
  mason::add_settings(
      family = stats::gaussian(),
      corstr = 'ar1',
      cluster.id = 'SID'
    ) %>%
  mason::add_variables("yvars", c("ACR", "eGFR")) %>% 
  mason::add_variables("xvars", "UDBP") %>% 
  mason::add_variables("covariates", 
                       c("VN", "ageBase", "Sex", "Ethnicity", "BMI", "fDM")) %>% 
  mason::construct() %>%
  mason::scrub()
```
